### 2019-12-19 Statistical Methods/07_hypothesis-testing.rmd
statistical methods
statistical methods

>>>>

Given that $\bar{X} = 78, \sigma^2 =25, n = 10, \alpha = 0.05$ test $H_0 : \mu \ge 80$, assuming that observations are randomly sampled from a normal distribution.

```{r, echo = T}
xbar <- 78; sigma <- 5; n <- 10
mu <- 80; alpha <- 0.05

# mu > 80 = left tail test

crit <- qnorm(alpha)

Z <- sqrt(n)*(xbar - mu)/sigma

ifelse(Z > crit, "Fail to reject the null", "Reject the null")

### 7.2

Repeat the previous exercise, but test $H_0 : \mu = 80$

```{r, echo = T}
xbar <- 78; sigma <- 5; n <- 10
mu <- 80; alpha <- 0.05

# mu = 80, two-tailed test

crit <- qnorm(1 - alpha/2)

Z <- sqrt(n)*(xbar - mu)/sigma

ifelse(abs(Z) <= crit, "Fail to reject the null", "Reject the null")

### 7.3

For the data in Exercise 1, compute a 0.95 confidence interval and verify that this interval is consistent with y our decision about whether to reject the null hypothesis $H_0 : \mu = 80$.

```{r, echo = T}
xbar <- 78; sigma <- 5; n <- 10
mu <- 80; alpha <- 0.05

xbar + qnorm(c(Lower = alpha/2, Upper = 1 - (alpha/2))) * sigma/sqrt(n)
```

_80_ is in the confidence interval, so fail to reject.

### 7.4

For exercise 1, determine the p-value.

### 7.5

For exercise 2, determine the p-value.

### 7.6

Given that $\bar{X} = 120, \sigma = 5, n = 49, \alpha = 0.05$, test $H_0 : \mu \ge 130$, assuming that observations are randomly sampled from a normal distribution.

### 7.7

Repeat the previous exercise but test $H_0 : \mu = 130$.

### 7.8

For the previous exercise, compute a 0.95 confidence interval and compare the result with your decision about whether to reject $H_0$.

### 7.9

If $\bar{X} = 23$ and $\alpha = 0.025$, can you make a decision about whether to reject $H_0 : \mu \le 25$ without knowing $\sigma$?

### 7.10
### 7.11
### 7.12
### 7.13
### 7.14
### 7.15
### 7.16
### 7.17
### 7.18
### 7.19

### 7.20
### 7.21
### 7.22
### 7.23
### 7.24
### 7.25
### 7.26
### 7.27
### 7.28
### 7.29

### 7.30
### 7.31
### 7.32
### 7.33
### 7.34
### 7.35
### 7.36
### 7.37
